{\Huge Supersymmetry} \\ \vspace{5mm} Lecture notes for FYS5190/FYS9190 Supersymmetry

### 2025-09-22 poincare.tex
Fixes for lecture nine

\df{We define the {\bf Pauli-Ljubanski polarisation vector} by:
\begin{equation}
W_\mu \equiv \frac{1}{2} \epsilon_\mu{}_ \nu{}_\rho{}_\sigma P^\nu M^{\rho\sigma}.
\end{equation}
where $ \epsilon_\mu{}_ \nu{}_\rho{}_\sigma$ is the totally antisymmetric Levi-Civita tensor with $ \epsilon_{0123}=1$.}
We can show that this vector is the one combination that is translation invariant, {\it i.e.}\ that it commutes with the translation operator,
\begin{equation}
[P_\mu, W_\nu]=0.
\label{eq:PW_commutator}
\end{equation}
This gives us two possibilities for Casimir invariants with the two Lorentz invariants $W_\mu P^\mu$ and $W_\mu W^\mu$, unfortunately from the definition of $W_\mu$ it is easy to see that  $W_\mu P^\mu=0$. However, the remaining option $W^2 = W_\mu W^\mu$ is a Casimir operator of the Poincaré algebra. While we argued from the Lorentz and translation invariance of the operators we can also show explicitly that
\begin{eqnarray}
[P_\mu, W^2] &=& 0,\\
{[M_\mu{}_\nu, W^2]} &=& 0.
\end{eqnarray}
The second of these relationships is not trivial to demonstrate. See \cite{IntrSUSY2010} for a complete proof. This exhausts the list of possibilities, and the Poincaré algebra is a rank-2 algebra. The $W_\mu$ do not in general commute among themselves, in fact 
\begin{equation}
[W_\mu,W_\nu]=\epsilon_{\mu\nu\rho\sigma}P^\rho W^\sigma.
\label{eq:WW_commutator}
\end{equation}
Thus, to find the full representation we can now look for states that are simultaneous eigenstates of $W^2$, $P^2$, the $P_\mu$, as well as one component of $W_\mu$.

We do this by starting from the representations of the translation subgroup with fixed eigenvalues $p_\mu$. What we are using here is know as the method of {\bf little groups} in physics. The idea is to consider the subgroup of the Poincare group that indeed leaves $p_\mu$ invariant: this is what is called the {\bf little group}.\footnote{In mathematics, it is often called the {\bf stabiliser subgroup}.} This will allow us to find unitary irreducible representations of the whole group from the unitary irreducible representations of the little group.  Because the behaviour of the little group is different depending on the value of $p_\mu$, we need to separate the problem into several discrete cases :
\begin{itemize}
\item[i)] $m=0$ and $p_\mu=(0,\mathbf 0)$
\item[ii)] $m=0$ and $p_\mu\neq(0,\mathbf 0)$
\item[iii)] $m^2>0$
\item[iv)] $m^2<0$
\end{itemize}

\paragraph{Case i)} Here, $P^2=0$ and $W^2=0$,\footnote{In the sense that their eigenvalues are always zero.} and there is only one representation $|0,0\rangle$. The little group that leaves $p_\mu=(0,\mathbf 0)$ invariant is the whole Lorentz group since boosts and rotations on a zero momentum point-like object just gives the same thing back. However, since the Lorentz group is not compact, we know that the only finite-dimensional unitary representation of the little group is the trivial representation. Thus this representation corresponds to the trivial representation for the Poincare group as well. We consider a state that transforms this way as the vacuum.

\paragraph{Case ii)} If we go to the rest frame of the particle, the states have momentum eigenvalues $p_\mu=(m, \mathbf 0)$.\footnote{This does not loose generality since the physics of the representation should be independent of frame.}  In this case, the little group turns out to be the group of rotations in three-dimensional space, $SO(3)$. To see this consider the Pauli-Ljubanski vector acting on such a state
\begin{equation}
W_i |m, p_\mu\rangle = \frac{1}{2} \epsilon_{i 0 jk}m M^{jk}  |m, p_\mu\rangle= -mJ_i  |m, p_\mu\rangle,
\label{eq:PL_restframe}
\end{equation}
where $J_i = \frac{1}{2} \epsilon_{ijk} M^{jk}$ is the {\bf spin operator} that forms the $\mathfrak{so}(3)\cong\mathfrak{su}(2)$ algebra. Since $WP=0$ we also have $W_0 = 0$ in this reference frame.\footnote{In the sense that $W_0$ has eigenvalue 0 for all states.} This gives $W^2 = -\mathbf W^2 = -m^2\mathbf J^2$.  So in this case we want to find the eigenstates of $W^2=-m^2J^2$ and one component of $W_\mu$ which we choose to be $W_3=-mJ_3$ with eigenvalue named $j_3$.

We already found the representations of  $\mathfrak{su}(2)$ in Sec.~\ref{sec:su2_rep}, so for this case we immediately know that in total the irreducible representations can be labeled by two numbers, $m^3\in\mathbb R$ and $j=0,\frac{1}{2},1,\frac{3}{2},\ldots$, as $|m,j\rangle$, and while each representation is infinite dimensional because it has continuous number for the momentum eigenvalues $p_\mu$, for each momentum eigenvalue it has has $2j+1$ spin states with $J_3$ eigenvalue $j_3=-j,-j+1,\ldots,j-1,j$, which we write as $|m,j,p_\mu,j_3\rangle$. 
Since the total spin operator acts on a state with spin $j$ as $\mathbf J^2| j\rangle=j(j+1)| j\rangle$, we also have that
\[W^2|m,j\rangle = -m^2 j(j+1)|m,j\rangle.\]

@@

\paragraph{Case iii)} We now want to look at massless particles, but  with non-zero $p_\mu$. Here we can not go to a rest frame and instead choose a frame such that $p_\mu=(p,0,0,p)$. We again have $P^2=0$  in the usual sense, and one can prove that $W_\mu$ and $P_\mu$ are proportional, $W_\mu=H P_\mu$. Thus $W^2=0$ and the proportionality factor  can be found from
\begin{eqnarray*}
W_0 |0, p_\mu\rangle &=& \frac{1}{2} \epsilon_{0 ijk}P^i M^{jk}  |0, p_\mu\rangle=P^i J_i  |0, p_\mu\rangle=\mathbf P\cdot\mathbf J |0, p_\mu\rangle, \\
P_0 |0, p_\mu\rangle &=& p |0, p_\mu\rangle,
\end{eqnarray*}
as 
\[ H = \frac{\mathbf P\cdot\mathbf J }{p}, \]
which is the definition of the {\bf helicity} of a massless particle.

The little group that leaves $p_\mu$ unchanged here is not so obvious to see. But it turns out to be given by the so-called special Euclidean group $SE(2)$, which consists of rotations and translations in two dimensional Euclidean space.
% Extend this by either discussing SE(2) earlier or proving the proportionality (see Zee VII.2).
The eigenvalues $h$ of $H$, $H|0,p_\mu\rangle=h|0,p_\mu\rangle$  can then be shown to be $h=\pm j_3$, where $j_3$ is another half-integer, $j_3=0,\half,1,\ldots$.

@@

This two-to-one correspondence means that $SO^+(1,3) \cong SL(2, \mathbb{C})/\mathbb{Z}_2$ and the groups have the same algebra, as discussed in Sec.~\ref{sec:Lorentz_group}. Thus we can look at the representations of $SL(2, \mathbb{C})$ instead of the  Lorentz group, when we describe spin-$\half$ particles,\footnote{We can of course also use the $SL(2, \mathbb{C})$ representations to construct representations for higher spin.} and working in $SL(2, \mathbb{C})$ is often easier. But what are those representations? It turns out that there are two inequivalent fundamental representations $\rho$ of $SL(2, \mathbb{C})$ in terms of $2\times2$ matrices $M\in SL(2, \mathbb{C})$:
\begin{enumerate}[i)]
\item The self-representation $\rho(M) = M$  acting on a member $\psi$ of a representation vector space $V$:
\[\psi'_A = M_A{}^B\psi_B,  \quad A, B = 1,2.\]
\item The complex conjugate self-representation $\rho(M) = M^*$ working on a vector $\bar{\psi}$ in a space $\dot V$:
\[\bar{\psi}'_{\dot{A}} = (M^*)_{\dot{A}}{}^{\dot{B}}\bar{\psi}_{\dot{B}}, \quad  \dot{A}, \dot{B} = 1,2.\]
\end{enumerate}
The indices here follow the same summation conventions as four-vectors. 
The vectors $\psi$ and $\bar{\psi}$ in these representation spaces are called, respectively, {\bf left- and right-handed Weyl spinors}, and the representation of the Lorentz group induced by the homomorphism is called the {\bf spinor representation}.
In addition to these two representations there are two dual representations, see Sec.~\ref{sec:dual_reps}, with $\rho(M)=M^{-1T}$ acting on vectors $\psi^A$ in $V^*$, the dual space of $V$, and $\rho(M)=M^{*-1T}$ acting on vectors  $\bar\psi^{\dot{A}}$ in $\dot{V}^*$, that are equivalent to i) and ii), respectively.

Indices can be lowered and raised with:
\begin{eqnarray}
\epsilon_{AB} &=& \epsilon_{\dot A \dot B} = \begin{pmatrix} 0 & -1\\ 1 & 0\end{pmatrix}, \label{eq:epsilonAB} \\
\epsilon^{AB} &=& \epsilon^{\dot{A}}{}^{\dot{B}} = \begin{pmatrix} 0 & 1\\ -1 & 0\end{pmatrix},\label{eq:epsilonAdotBdot}
\end{eqnarray}
which work as maps between the dual spaces.
The dots on the indices for the complex conjugate representation are there to help us remember which representation we are using and does not carry any additional importance, other than being a different index.

Since (\ref{eq:MofLambda}) gives $M$ in terms of the Pauli matrices, their index structure must be $\bar{\sigma^\mu}^{\dot{A}A}$ and $\sigma^\mu_{A\dot{A}}$. 
For a consistent index notation, the relationship between the vectors $\psi$ and $\bar{\psi}$ can be expressed with:
\[  \psi^A = \bar\psi_{\dot{A}}^*\bar{\sigma}^{0\dot{A}A}, \quad  \psi_A = {\sigma}^0_{A\dot{A}}\bar\psi^{\dot{A}*}, \quad  \bar{\psi}^{\dot{A}} = \bar{\sigma}^{0\dot{A}A}\psi_A^*, \quad \text{and}\quad  \bar{\psi}_{\dot{A}} =\psi^{A*} \sigma^0_{A\dot{A}} .\]
This may seem as a bit of an overkill in indices as the sigma matrices involved are the identity: $\bar{\sigma}^{0\dot{A}A} = \delta^{\dot{A}A}$ and  $\sigma^0_{A\dot{A}} = \delta_{A\dot{A}}$, and we will in the following often omit the $\sigma^0$ matrix and simply write $(\psi_A)^* = \bar{\psi}^{\dot{A}}$ and similarly.
Note that from the above the following relationships hold for the hermitian conjugate when we ignore the $\sigma^0$ matrices that keep track of the indices:
\begin{eqnarray}
(\psi_A)^\dagger &=& \bar{\psi}_{\dot{A}} \\
(\bar{\psi}_{\dot{A}})^\dagger &=& \psi_A. \label{eq:Weyl_hc}
\end{eqnarray}

We further define contractions of Weyl spinors that are invariant under $SL(2,\mathbb{C})$ transformations -- just as  contractions of four-vectors are invariant under Lorentz transformations -- as follows:
\df{The contraction of two Weyl spinors $\psi$ and $\chi$ is given by $\psi\chi \equiv \psi ^A \chi_A$ and $\bar{\psi}\bar{\chi} \equiv \bar{\psi}_{\dot{A}}\bar{\chi}^{\dot{A}}$.}
With this in hand we see that 
\[\psi^2 \equiv \psi \psi = \psi^A\psi_A = \epsilon^{AB}\psi_B\psi_A = \epsilon^{12}\psi_2\psi_1 + \epsilon^{21}\psi_1\psi_2 = \psi_2\psi_1 - \psi_1\psi_2.\]
This quantity is zero if the Weyl spinors commute. In order to avoid this we make the following assumption which is consistent with how we treat fermions as anti-commuting operators:
\post{All Weyl spinors anticommute:\footnote{This means that Weyl spinors are so-called {\bf Grassmann numbers}.}
 $\{\psi_A ,\psi_B\} = \{\bar{\psi}_{\dot{A}}, \bar{\psi}_{\dot{B}}\} = \{\psi_A, \bar{\psi}_{\dot{B}}\} = \{\bar{\psi}_{\dot{A}}, \psi_B\} = 0$.}
This means that the contraction evaluates as
\[\psi^2 \equiv \psi \psi = \psi^A\psi_A = -2 \psi_1\psi_2.\]

%%%
\subsection{Useful relationships for Weyl spinors}
\label{sec:Weylspinor_calc}
%%%
For Weyl spinors $\psi$, $\eta$, and $\phi$ we can prove the following relationships\footnote{For clarity we have inserted parenthesis to show the different contractions.} 
\begin{eqnarray}
\eta\psi 				&=& \psi\eta,  \label{eq:Weylspinor_etapsi}  \\
\bar\eta\bar\psi 			&=& \bar\psi\bar\eta, \label{eq:Weylspinor_contraction_order_bared} \\
(\eta\psi)^\dagger 		&=& \bar\psi\bar\eta,  \\
(\eta\psi)(\eta\phi) 		&=& -\frac{1}{2}(\eta\eta)(\psi\phi), \label{eq:Weylspinor_etapsietapsi}  \\
\eta\sigma^\mu\bar\psi 	&=& - \bar\psi\bar\sigma^\mu\eta,  \label{eq:Weylspinor_etasigmapsi} \\
(\sigma^\mu \bar{\eta})_A(\eta\sigma^\nu \bar{\eta})&=&\frac{1}{2}g^{\mu\nu}\eta_A(\bar{\eta}\bar{\eta}), \label{eq:Weylspinor_sigmaetaetasigmaeta}\\
(\eta\sigma^\mu \bar{\eta})(\eta\sigma^\nu \bar{\eta})&=&\frac{1}{2}g^{\mu\nu}(\eta\eta)(\bar{\eta}\bar{\eta}),   \label{eq:Weylspinor_etasigmamuetaetasigmanueta} \\
(\eta\sigma^\mu\partial_\mu \bar\psi )(\eta\psi) &=& -\frac{1}{2}(\psi\sigma^\mu\partial_\mu \bar\psi)(\eta\eta),\\
(\partial_\mu\psi\sigma^\mu \bar\eta)(\bar\eta\bar\psi) &=& -\frac{1}{2}(\partial_\mu\psi\sigma^\mu \bar\psi)(\bar\eta\bar\eta), \label{eq:Weylspinor_last} \\
\eta\sigma^{\mu\nu}\psi	&=&-\psi\sigma^{\mu\nu}\eta.   \label{eq:Weylspinor_etasigmamunupsi} 
\end{eqnarray}
Here $\sigma^{\mu\nu} = \frac{i}{4}(\sigma^\mu \bar{\sigma}^\nu - \sigma^\nu \bar{\sigma}^\mu)$.

%%%
\subsection{Dirac spinors}
\label{sec:Dirac_spinors}
%%%

The Weyl spinors can in turn be used in a four-dimensional representation of the Poincaré group for spin-$\half$ fermions, stacking two Weyl different spinors, one from the self-representation $\phi_A$, and one from the complex conjugate,  $\bar{\chi}^{\dot{A}}$, into a four-component {\bf Dirac spinor} $\psi_a$, 
\begin{equation*}
\psi_a = \begin{pmatrix}\phi_A\\ \bar{\chi}^{\dot{A}}\end{pmatrix},
\end{equation*}
making a new vector space that is a direct sum of the two vector spaces $W=V\oplus \dot{V}^*$.
Here, we have in general $(\phi_A)^* \neq \bar{\chi}^{\dot{A}}$. In order to describe a Dirac fermion, which has both particle and antiparticle states, using this Dirac spinor we need two distinct Weyl spinors with different handedness. For Majorana fermions that are their own antiparticles we can instead use the simpler:
\[\psi_a = \begin{pmatrix} \psi_A \\ \bar{\psi}^{\dot{A}}\end{pmatrix}.\]
The representation of $SL(2,\mathbb{C})$ on $W$ is
\[ \rho(M)=\left[\begin{matrix} M & 0 \\ 0 & M^{*-1T} \end{matrix}\right]. \]
% Discuss parity here? See see Wiedemann 1.4

@@

We define a bared version of the Dirac spinor by  $\bar\psi \equiv \psi^\dagger\gamma^0$, which can be written in terms of Weyl spinors as 
\begin{equation*}
\bar\psi  =\begin{pmatrix}\phi_A^\dagger & \bar{\chi}^{\dot{A}^\dagger}\end{pmatrix} \left(\begin{matrix} 0 & \sigma^0_{A\dot{A}} \\ \bar\sigma^{0\dot A A} & 0 \end{matrix}\right)
= \begin{pmatrix}  \bar{\chi}^{\dot{A}*}\bar\sigma^{0\dot A A}  & \phi_A^*  \sigma^0_{A\dot{A}} \end{pmatrix}
= \begin{pmatrix}  \chi^A & \bar{\phi}_{\dot A} \end{pmatrix}.
\end{equation*}

%%%
\subsection{Dirac and Weyl equations}
\label{sec:fermion_eoms}
%%%

>>>>

\df{We define the {\bf Pauli-Ljubanski polarisation vector} by:
\begin{equation}
W_\mu \equiv \frac{1}{2} \epsilon_\mu{}_ \nu{}_\rho{}_\sigma P^\nu M^{\rho\sigma}.
\end{equation}
where $ \epsilon_\mu{}_ \nu{}_\rho{}_\sigma$ is the totally antisymmetric Levi-Civita tensor with $ \epsilon_{0123}=1$.}
We can show that this vector is the one combination that is translation invariant, {\it i.e.}\ that it commutes with the translation operator,
\begin{equation}
[P_\mu, W_\nu]=0.
\label{eq:PW_commutator}
\end{equation}
This gives us two possibilities for Casimir invariants with the two Lorentz invariants $W_\mu P^\mu$ and $W_\mu W^\mu$, unfortunately from the definition of $W_\mu$ it is easy to see that  $W_\mu P^\mu=0$. However, the remaining option $W^2 = W_\mu W^\mu$ is a Casimir operator of the Poincaré algebra. While we argued from the Lorentz and translation invariance of the operators we can also show explicitly that
\begin{eqnarray}
[P_\mu, W^2] &=& 0,\\
{[M_\mu{}_\nu, W^2]} &=& 0.
\end{eqnarray}
The second of these relationships is not trivial to demonstrate. See \cite{IntrSUSY2010} for a complete proof. This exhausts the list of possibilities, and the Poincaré algebra is a rank-2 algebra.

The $W_\mu$ do not in general commute among themselves, in fact 
\begin{equation}
[W_\mu,W_\nu]=\epsilon_{\mu\nu\rho\sigma}P^\rho W^\sigma.
\label{eq:WW_commutator}
\end{equation}
Thus, to find the full representation we can now look for states that are simultaneous eigenstates of $W^2$, $P^2$, the $P_\mu$, as well as one component of $W_\mu$.

We do this by starting from the representations of the translation subgroup with fixed eigenvalues $p_\mu$. What we are using here is know as the method of {\bf little groups} in physics. The idea is to consider the subgroup of the Poincaré group that indeed leaves $p_\mu$ invariant: this is what is called the {\bf little group}.\footnote{In mathematics, it is often called the {\bf stabiliser subgroup}.}  This will allow us to find unitary irreducible representations of the whole group from the unitary irreducible representations of the little group.  Because the behaviour of the little group is different depending on the value of $p_\mu$, we need to separate the problem into several discrete cases :
\begin{itemize}
\item[i)] $m=0$ and $p_\mu=(0,\mathbf 0)$
\item[ii)] $m=0$ and $p_\mu\neq(0,\mathbf 0)$
\item[iii)] $m^2>0$
\item[iv)] $m^2<0$
\end{itemize}

\paragraph{Case i)} Here, $P^2=0$ and $W^2=0$,\footnote{In the sense that their eigenvalues are always zero.} and there is only one representation $|0,0\rangle$. The little group that leaves $p_\mu=(0,\mathbf 0)$ invariant is the whole Lorentz group $SO^+(1,3)$ generated by the Lorentz group generators $M_{\mu\nu}$, since boosts and rotations on a zero momentum point-like object just gives the same thing back. However, since the Lorentz group is not compact, we know that the only finite-dimensional unitary representation of the little group is the trivial representation. Thus this representation corresponds to the trivial representation for the Poincaré group as well. We consider a state that transforms this way as the vacuum.

\paragraph{Case iii)} If we go to the rest frame of the particle, the states have momentum eigenvalues $p_\mu=(m, \mathbf 0)$.\footnote{This does not loose generality since the physics of the representation should be independent of frame.}  In this case, the little group turns out to be the group of rotations in three-dimensional space, $SO(3)$. To see this consider the Pauli-Ljubanski vector acting on such a state
\begin{equation}
W_i |m, p_\mu\rangle = \frac{1}{2} \epsilon_{i 0 jk}m M^{jk}  |m, p_\mu\rangle= -mJ_i  |m, p_\mu\rangle,
\label{eq:PL_restframe}
\end{equation}
where $J_i = \frac{1}{2} \epsilon_{ijk} M^{jk}$ is the {\bf spin operator} that forms the $\mathfrak{so}(3)\cong\mathfrak{su}(2)$ algebra. Since $WP=0$ we also have $W_0 = 0$ in this reference frame.\footnote{In the sense that $W_0$ has eigenvalue 0 for all states.} This gives $W^2 = -\mathbf W^2 = -m^2\mathbf J^2$.  So in this case we want to find the eigenstates of $W^2=-m^2J^2$ and one component of $W_\mu$ which we choose to be $W_3=-mJ_3$ with eigenvalue named $j_3$.

We already found the representations of  $\mathfrak{su}(2)$ in Sec.~\ref{sec:su2_rep}, so for this case we immediately know that in total the irreducible representations can be labeled by two numbers, $m^2\in\mathbb R$ and $j=0,\frac{1}{2},1,\frac{3}{2},\ldots$, as $|m,j\rangle$, and while each representation is infinite dimensional because it has continuous number for the momentum eigenvalues $p_\mu$, for each momentum eigenvalue it has has $2j+1$ spin states with $J_3$ eigenvalue $j_3=-j,-j+1,\ldots,j-1,j$, which we write as $|m,j,p_\mu,j_3\rangle$. 
Since the total spin operator acts on a state with spin $j$ as $\mathbf J^2| j\rangle=j(j+1)| j\rangle$, we also have that
\[W^2|m,j\rangle = -m^2 j(j+1)|m,j\rangle.\]

@@

\paragraph{Case ii)} We now want to look at massless particles, but  with non-zero $p_\mu$. Here we can not go to a rest frame and instead choose a frame such that $p_\mu=(p,0,0,p)$. We again have $P^2=0$  in the usual sense, and one can prove that $W_\mu$ and $P_\mu$ are proportional, $W_\mu=H P_\mu$. Thus $W^2=0$ and the proportionality factor  can be found from
\begin{eqnarray*}
W_0 |0, p_\mu\rangle &=& \frac{1}{2} \epsilon_{0 ijk}P^i M^{jk}  |0, p_\mu\rangle=P^i J_i  |0, p_\mu\rangle=\mathbf P\cdot\mathbf J |0, p_\mu\rangle, \\
P_0 |0, p_\mu\rangle &=& p |0, p_\mu\rangle,
\end{eqnarray*}
as 
\[ H = \frac{\mathbf P\cdot\mathbf J }{p}, \]
which is the definition of the {\bf helicity} of a massless particle.

The little group that leaves $p_\mu$ unchanged here is not so obvious to see. But it turns out to be given by the special Euclidean group $SE(2)$, which consists of rotations and translations in two dimensional Euclidean space.
% Extend this by either discussing SE(2) earlier or proving the proportionality (see Zee VII.2).
The eigenvalues $h$ of $H$, $H|0,p_\mu\rangle=h|0,p_\mu\rangle$  can then be shown to be $h=\pm j_3$, where $j_3$ is another half-integer, $j_3=0,\half,1,\ldots$.

@@

This two-to-one correspondence means that $SO^+(1,3) \cong SL(2, \mathbb{C})/\mathbb{Z}_2$ and the groups have the same algebra, as discussed in Sec.~\ref{sec:Lorentz_group}. Thus we can look at the representations of $SL(2, \mathbb{C})$ instead of the  Lorentz group, when we describe spin-$\half$ particles,\footnote{We can of course also use the $SL(2, \mathbb{C})$ representations to construct representations for higher spin.} and working in $SL(2, \mathbb{C})$ is often easier. But what are those representations? It turns out that there are two inequivalent fundamental representations $\rho$ of $SL(2, \mathbb{C})$ in terms of $2\times2$ matrices $M\in SL(2, \mathbb{C})$:\footnote{There is no similarity transform between them.}
\begin{enumerate}[i)]
\item The self-representation $\rho(M) = M$  acting on a member $\psi$ of a representation vector space $V$:
\[\psi'_A = M_A{}^B\psi_B,  \quad A, B = 1,2.\]
\item The complex conjugate self-representation $\rho(M) = M^*$ working on a vector $\bar{\psi}$ in a space $\dot V$:
\[\bar{\psi}'_{\dot{A}} = (M^*)_{\dot{A}}{}^{\dot{B}}\bar{\psi}_{\dot{B}}, \quad  \dot{A}, \dot{B} = 1,2.\]
\end{enumerate}
The indices here follow the same summation conventions as four-vectors. 
The vectors $\psi$ and $\bar{\psi}$ in these representation spaces are called, respectively, {\bf left- and right-handed Weyl spinors}. The representations of the Lorentz group induced by the homomorphism are called the {\bf spinor representations}, and the two different  representations are often called the $(\half,0)$ and $(0,\half)$ representations, respectively.
In addition to these two representations there are two dual representations, see Sec.~\ref{sec:dual_reps}, with $\rho(M)=M^{-1T}$ acting on vectors $\psi^A$ in $V^*$, the dual space of $V$, and $\rho(M)=M^{-1\dagger}$ acting on vectors  $\bar\psi^{\dot{A}}$ in $\dot{V}^*$, that are equivalent to i) and ii), respectively.

Indices can be lowered and raised with the tensors:
\begin{eqnarray}
\epsilon_{AB} &=& \epsilon_{\dot A \dot B} = \begin{pmatrix} 0 & -1\\ 1 & 0\end{pmatrix}, \label{eq:epsilonAB} \\
\epsilon^{AB} &=& \epsilon^{\dot{A}}{}^{\dot{B}} = \begin{pmatrix} 0 & 1\\ -1 & 0\end{pmatrix},\label{eq:epsilonAdotBdot}
\end{eqnarray}
which work as maps between the dual spaces.
The dots on the indices for the complex conjugate representation are there to help us remember which representation we are using and does not carry any additional importance, other than being a different index.

Since (\ref{eq:MofLambda}) gives $M$ in terms of the Pauli matrices, their index structure must be $\bar{\sigma}^{\mu\dot{A}A}$ and $\sigma^\mu_{A\dot{A}}$. 
For a consistent index notation, the relationship between the vectors $\psi$ and $\bar{\psi}$ can be expressed with:
\[  \psi^A = \bar\psi_{\dot{A}}^*\bar{\sigma}^{0\dot{A}A}, \quad  \psi_A = {\sigma}^0_{A\dot{A}}\bar\psi^{\dot{A}*}, \quad  \bar{\psi}^{\dot{A}} = \bar{\sigma}^{0\dot{A}A}\psi_A^*, \quad \text{and}\quad  \bar{\psi}_{\dot{A}} =\psi^{A*} \sigma^0_{A\dot{A}} .\]
This may seem as a bit of an overkill in indices as the sigma matrices involved are the identity: $\bar{\sigma}^{0\dot{A}A} = \delta^{\dot{A}A}$ and  $\sigma^0_{A\dot{A}} = \delta_{A\dot{A}}$, and we will in the following often omit the $\sigma^0$ matrix and simply write $(\psi_A)^* = \bar{\psi}^{\dot{A}}$ and similarly. This means that $\psi^A$ and $\bar{\psi}_{\dot{A}}$ should be read as row-vectors, while $\psi_A$ and $\bar{\psi}^{\dot{A}}$ are column-vectors.
From the above the following relationships hold for the hermitian conjugate when we ignore the $\sigma^0$ matrices that keep track of the indices:
\begin{eqnarray}
(\psi_A)^\dagger &=& \bar{\psi}_{\dot{A}}, \\
(\bar{\psi}_{\dot{A}})^\dagger &=& \psi_A, \label{eq:Weyl_hc}
\end{eqnarray}
which is a map between the two distinct representations.

We further define contractions of Weyl spinors that are invariant under $SL(2,\mathbb{C})$ transformations---just as  contractions of four-vectors are invariant under Lorentz transformations---as follows:
\df{The {\bf contraction} of two Weyl spinors $\psi$ and $\chi$ is given by $\psi\chi \equiv \psi^A \chi_A$ and $\bar{\psi}\bar{\chi} \equiv \bar{\psi}_{\dot{A}}\bar{\chi}^{\dot{A}}$.}
With this in hand we see that 
\[\psi^2 \equiv \psi \psi = \psi^A\psi_A = \epsilon^{AB}\psi_B\psi_A = \epsilon^{12}\psi_2\psi_1 + \epsilon^{21}\psi_1\psi_2 = \psi_2\psi_1 - \psi_1\psi_2.\]
This quantity is zero if the Weyl spinor components commute. When we use Weyl spinors in quantum field theory to represent fermions we avoid this by making the following assumption which is consistent with how we treat fermions as anti-commuting operators:
\post{All Weyl spinor (components) representing fermions anticommute:\footnote{This means that these Weyl spinor components are so-called {\bf Grassmann numbers}.}
 $\{\psi_A ,\psi_B\} = \{\bar{\psi}_{\dot{A}}, \bar{\psi}_{\dot{B}}\} = \{\psi_A, \bar{\psi}_{\dot{B}}\} = \{\bar{\psi}_{\dot{A}}, \psi_B\} = 0$.}
Then the contraction evaluates as
\[\psi^2 \equiv \psi \psi = \psi^A\psi_A = -2 \psi_1\psi_2.\]

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Useful relationships for Weyl spinors}
\label{sec:Weylspinor_calc}
%%%%%%%%%%%%%%%%%%%%%%%%%%
For Weyl spinors $\psi$, $\eta$, and $\phi$ with anti-commuting components we can prove the following relationships\footnote{For clarity we have inserted parenthesis to show the different contractions.} 
\begin{eqnarray}
\eta\psi 				&=& \psi\eta,  \label{eq:Weylspinor_etapsi}  \\
\bar\eta\bar\psi 			&=& \bar\psi\bar\eta, \label{eq:Weylspinor_contraction_order_bared} \\
(\eta\psi)^\dagger 		&=& \bar\psi\bar\eta,  \\
(\eta\psi)(\eta\phi) 		&=& -\frac{1}{2}(\eta\eta)(\psi\phi), \label{eq:Weylspinor_etapsietapsi}  \\
\eta\sigma^\mu\bar\psi 	&=& - \bar\psi\bar\sigma^\mu\eta,  \label{eq:Weylspinor_etasigmapsi} \\
(\sigma^\mu \bar{\eta})_A(\eta\sigma^\nu \bar{\eta})&=&\frac{1}{2}g^{\mu\nu}\eta_A(\bar{\eta}\bar{\eta}), \label{eq:Weylspinor_sigmaetaetasigmaeta}\\
(\eta\sigma^\mu \bar{\eta})(\eta\sigma^\nu \bar{\eta})&=&\frac{1}{2}g^{\mu\nu}(\eta\eta)(\bar{\eta}\bar{\eta}),   \label{eq:Weylspinor_etasigmamuetaetasigmanueta} \\
(\eta\sigma^\mu\partial_\mu \bar\psi )(\eta\psi) &=& -\frac{1}{2}(\psi\sigma^\mu\partial_\mu \bar\psi)(\eta\eta),\\
(\partial_\mu\psi\sigma^\mu \bar\eta)(\bar\eta\bar\psi) &=& -\frac{1}{2}(\partial_\mu\psi\sigma^\mu \bar\psi)(\bar\eta\bar\eta), \label{eq:Weylspinor_last} \\
\eta\sigma^{\mu\nu}\psi	&=&-\psi\sigma^{\mu\nu}\eta.   \label{eq:Weylspinor_etasigmamunupsi} 
\end{eqnarray}
Here,  we have used the rank-2 tensor
\begin{equation*}
\sigma^{\mu\nu} \equiv \frac{i}{4}(\sigma^\mu \bar{\sigma}^\nu - \sigma^\nu \bar{\sigma}^\mu).
\end{equation*}
More details on Weyl-spinors and further spinor relationships can be found in~\cite{Dreiner:2008tw}.\footnote{Note that there are some differences in notation.}

%%%%%%%%%%%%%
\subsection{Dirac spinors}
\label{sec:Dirac_spinors}
%%%%%%%%%%%%%

The Weyl spinors can in turn be used in a four-dimensional representation of the Poincaré group for spin-$\half$ fermions, stacking two Weyl different spinors, one from the self-representation $\phi_A$, and one from the complex conjugate,  $\bar{\chi}^{\dot{A}}$, into a four-component {\bf Dirac spinor} $\psi_a$, 
\begin{equation*}
\psi_a = \begin{pmatrix}\phi_A\\ \bar{\chi}^{\dot{A}}\end{pmatrix},\quad a=1,2,3,4,
\end{equation*}
making a new vector space that is a direct sum of the two vector spaces $W=V\oplus \dot{V}^*$. We index Dirac spinors with lower case latin indices, traditionally starting at the beginning of the alphabet.
In order to describe a Dirac fermion, which has both particle and antiparticle states, using this Dirac spinor we need two distinct Weyl spinors with different handedness. Thus, we have in general $(\phi_A)^* \neq \bar{\chi}^{\dot{A}}$.  For Majorana fermions that are their own antiparticles we can instead use the simpler:
\[\psi_a = \begin{pmatrix} \psi_A \\ \bar{\psi}^{\dot{A}}\end{pmatrix}, \quad a=1,2,3,4.\]
The representation of $SL(2,\mathbb{C})$ on $W$ is
\[ \rho(M)=\left[\begin{matrix} M & 0 \\ 0 & M^{-1 \dagger} \end{matrix}\right]. \]
% Discuss parity here? See see Wiedemann 1.4

@@

We define a bared version of the Dirac spinor by  $\bar\psi \equiv \psi^\dagger\gamma^0$, which can be written in terms of Weyl spinors as 
\begin{equation*}
\bar\psi^a  =\begin{pmatrix}\phi_A^\dagger & \bar{\chi}^{\dot{A}^\dagger}\end{pmatrix} \left(\begin{matrix} 0 & \sigma^0_{A\dot{A}} \\ \bar\sigma^{0\dot A A} & 0 \end{matrix}\right)
= \begin{pmatrix}  \bar{\chi}^{\dot{A}*}\bar\sigma^{0\dot A A}  & \phi_A^*  \sigma^0_{A\dot{A}} \end{pmatrix}
= \begin{pmatrix}  \chi^A & \bar{\phi}_{\dot A} \end{pmatrix}.
\end{equation*}
Observe that the bared Dirac spinors are row vectors. These transform under the representation
\[ \rho(M)=\left[\begin{matrix} M^{-1} & 0 \\ 0 & M^\dagger \end{matrix}\right]. \]
The contraction of two Dirac spinors is then
\[ \bar\psi \psi \equiv \bar\psi^a \psi_a = \chi^A  \phi_A   + \bar{\phi}_{\dot A} \bar{\chi}^{\dot{A}} =\phi\chi +\bar\phi\bar\chi.\]

%%%%%%%%%%%%%%%%%%%%
\subsection{Dirac and Weyl equations}
\label{sec:fermion_eoms}
%%%%%%%%%%%%%%%%%%%%
